\documentclass[a4paper,12pt]{report}

\usepackage{cmap} % поиск в документе
\usepackage[T2A]{fontenc} % кодировка
\usepackage[utf8]{inputenc} % кодировка исходного текста
\usepackage[english, russian]{babel} % локализация и переносы

\usepackage{mathtext} % матшрифт

\usepackage{indentfirst} % отступ после заголовка
\usepackage{csquotes}

\author{Kolobov Kirill}
\title{First semester test}
\date{11 November 2020}

\begin{document}

\maketitle

\section*{Task 1. Present Simple or Present Continuous}
\begin{enumerate}
    \item{Look! Pauline is watering the flowers.}
    \item{Listen! The girls are singing a song.}
    \item{She usually comes home by bus.}
    \item{Jack goes to his grandmother every day.}
    \item{Look! Sally and Joe are playing tennis.}
    \item{Nelly drinks a cup of tea every morning.}
    \item{We can't play tennis. It is raining now.} 
    \item{Bill is doing his homework at the moment.}
    \item{Jane always does her homework in her room.}
    \item{The boys sometimes run to the park.} 
    \item{My cat never sleeps in my room.}
    \item{Listen! Phil is singning an English song.}
    \item{No, I do not listen to music on my mobile phone, I have a bath.}
    \item{Michael can't play football. He is playing guitar at the moment.}
    \item{We never write letters to America.}
\end{enumerate}

\section*{Task 2. Complex and mixed}
\begin{enumerate}
    \item{He usually goes to school by bus, but today he is walking to school.}
    \item{Listen! The birds are singing. They always sing in the morning.} 
    \item{What are you doing? you always Do you always work like that?}
    \item{I don’t swim in this lake! It is far too cold.}
    \item{Peter hss just eaten his school dinner, but I think school dinners taste horrible.}
    \item{The girls often do their homework together, but today they aren’t doing their homework properly!}
    \item{I sometimes go for a walk in the afternoons, but today I am working instead.}
    \item{Christiana always feeds her cows in the morning, but Tim is feeding them today.}
    \item{Look! isn’t being that Sarah? She is just going into the cinema with her boyfriend.} 
    \item{Dad doesn’t know that Tom has run in a marathon today. He will be surprised.}
\end{enumerate}

\section*{Task 3. Modal verbs}
\begin{enumerate}
    \item{The cake must be almost ready now. – Are you sure? – Yes, practically.}
    \item{You should put sausage, cucumber, onion, potatoes, eggs and sour cream to make the Russian salad tasty.}
    \item{May you have failed to put sugar and vinegar in the biscuit again? How can you be so careless?}
    \item{You may take the fork, knife and plate. I don’t need it any more.}
    \item{The beefsteak can’t be so raw and untasty. I’ve cooked it properly!}
    \item{Should I buy a loaf of bread or some curds?}
    \item{No, you shouldn’t eat ice-cream in the street in winter.}
    \item{Can it be that the pork was spoiled?}
    \item{Could you show me how to slice the cabbage and carrots for this soup.}
    \item{You could have cooked lunch before our arrival.}
    \item{You’ve over fried the potatoes. You should be more accurate about cooking.}
    \item{Don’t put too much salt in the dough. We can spoil everything.}
    \item{Can it be that the child has eaten so much candies?}
    \item{Don’t you know that one mustn’t eat milk and cucumbers?}
\end{enumerate}

\section*{Task 4. True or False}
\begin{enumerate}
    \item{Polytechnic first appeared in the mid 1960th -- \textbf{TRUE}}
    \item{Polytechnics are universities which teach technical courses -- \textbf{FALSE}}
    \item{Undergraduates enjoy interesting life at a polytechnics -- \textbf{TRUE}}
    \item{At a polytechnic students can only study in the evening after their work -- \textbf{FALSE}}
    \item{Polytechnics are special colleges which teach students at a university level -- \textbf{FALSE}}
    \item{Polytechnics are very different from universities -- \textbf{FALSE}}
    \item{Polytechnics have as many courses as any university. -- \textbf{TRUE}}
\end{enumerate}

\section*{Task 5. Short summary}
I have hoped until recently that the University will give me useful knowlegde enough to be a professional developer in the future. 
Well... There's a lot of useless subjects that I am expected to do. 
I hate a project activity here. 
I will never(!) work in a factory, why a should do this?..

Somewhere exams in the University are pretty futile. 
One should just mug some text up to get the highest mark, 
but he is not to know anything. Just cram.

Now I want to learn how to work in \LaTeX~better. 
I have enough knowledge to work in it freely but I want to get master there. 
I wished Alexey Kharlamenkov will help me but he knows nothing about \LaTeX.

OK, student's life... hm... 
There's COVID-19 and, well, 
I don't want to have a <<student's life>> as you mean. 
I am known to be the different.

\begin{center}
    \textit{Il est libre, en effet. En vrai chevalier français}
\end{center}
\end{document}
